\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{geometry}
\usepackage{fancyhdr}
\usepackage{graphicx}
\usepackage{minted}
\usepackage{hyperref}
\usepackage{fontspec}

% document settings start
\geometry{a4paper, margin=0.9in}
\graphicspath{{./outputs/}}
\usemintedstyle{bw}
\pagestyle{fancy}
\fancyhf{}
\lhead{Java Programming}
\rhead{Asim Bera}
\lfoot{\href{https://github.com/asimbera/ccp-assignments.git}{https://github.com/asimbera/ccp-assignments.git}}
\rfoot{Page \thepage}

\hypersetup{
colorlinks=true,
linkcolor=blue,
filecolor=magenta,
urlcolor=blue,
}
\urlstyle{same}

\setmainfont{Comfortaa}
\setmonofont{FantasqueSansMono Nerd Font}

\input{./macro}
% document settings end

\begin{document}
\input{./cover}
\newpage
\pagenumbering{roman}
\tableofcontents
\newpage
\pagenumbering{arabic}
\setcounter{page}{1}
\section{Java Assignment}
\problem{Q01}{Print the average of three numbers entered by user by creating a class named "Average" having a method to calculate and print the average.}
\problem{Q02}{Print the sum, differences, and product of two complex numbers by creating a class named "Complex" with separate methods for each operation whose real and imaginary part is to  be entered by the user.}
\problem{Q03}{Write a program that would print the information (name, year of joining, salary, address) of three employees by creating a class "Employee". The output should be in a tabular form.}
\problem{Q04}{Write a program to input the details of a student using constructor and display the same.}
\problem{Q05}{Write a program to print the information of three employees by creating a class "Employee" and show the details of all three Employees  using Abstract class.}
\problem{Q06}{Write a program to give the example  for "this" operator. And also use the "this" keyword as a return statement.}
\problem{Q07}{Write a program to add all the elements of a One-Dimensional array.}
\problem{Q08}{Write a program to reverse the elements of a One-Dimensional array.}
\problem{Q09}{Write a program to perform addition,  subtraction, multiplication, and division of two One-Dimensional arrays.}
\problem{Q10}{Write a program to perform addition  of two Two-Dimensional arrays.}
\problem{Q11}{Write a program to take a string as input and display the string and its length. (Using String Functions).}
\problem{Q12}{Write a program to check whether the inputted String is a Palindrome String or not.}
\problem{Q13}{Write a program to count the total number of characters in a string.}
\problem{Q14}{Write a program to count the total number of vowels and consonants in a string.}
\problem{Q15}{Write a program to remove all the white spaces from a string.}
\problem{Q16}{Write a program to find the duplicate characters in a string.}
\problem{Q17}{Write a program to swap two string variables without using third or temp variable.}
\problem{Q18}{Write a program that accepts a shopping list of five items from the command line and stores them in a vector.}
\problem{Q19}{Modify the program of previous problem to accomplish the following: \\
To delete an item in the list.\\
To add an item at a specified location in the list.\\
To add an item at the end of the list.\\
To print the contents of the vector.}

\end{document}
