\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{geometry}
\usepackage{fancyhdr}
\usepackage{graphicx}
\usepackage{minted}
\usepackage{hyperref}

% document settings start
\geometry{a4paper, margin=0.9in}
\graphicspath{{./outputs/}}

\pagestyle{fancy}
\fancyhf{}
\lhead{Programming in C}
\rhead{Asim Bera}
\lfoot{\href{https://github.com/asimbera/ccp-assignments.git}{View on Github}}
\rfoot{Page \thepage}

\hypersetup{
colorlinks=true,
linkcolor=blue,
filecolor=magenta,
urlcolor=blue,
}
\urlstyle{same}

\input{../macro}
% document settings end

\begin{document}
\input{../cover}
\newpage
\tableofcontents
\newpage

\section{C Basics : Input \& Outputs}

\problem{01}{Write a C program to perform input/output of all basic data types.}
\problem{02}{Write a C program to enter two numbers and find their sum.}
\problem{03}{Write a C program to enter two numbers and perform all arithmetic operations.}
\problem{04}{Write a C program to enter length and breadth of a rectangle and find its perimeter.}
\problem{05}{Write a C program to enter length and breadth of a rectangle and find its area.}
\problem{06}{Write a C program to enter radius of a circle find its diameter, circumference and area.}
\problem{07}{Write a program to enter length in cm and convrt it into meter and kilometer.}
\problem{08}{Write a program to enter temperature in Celsius and convert it into Farenheit.}
\problem{09}{Write a program to enter temperature in Farenheit and convert it into Celsius.}
\problem{10}{Write a C program to convert days into years, weeks and days.}
\problem{11}{Write a C program to find xy of any number x and power y.}
\problem{12}{Write a C program to enter any number and calculate its square root.}
\problem{13}{Write a C program to enter two angles of a triangle and find its third angle.}
\problem{14}{Write a C program to enter base and height of a triangle and find its area.}
\problem{15}{Write a C program to calculate area of an equilateral triangle.}
\problem{16}{Write a C program to enter marks of five subjects and calculate total, average and percentage.}
\problem{17}{Write a C program to enter P, T, R and calculate Simple Interest.}
\problem{18}{Write a C program to enter P, T, R and calculate Compound Interest.}

\end{document}

