\documentclass{article}
\usepackage{geometry}
\usepackage{minted}

% document settings start
\geometry{a4paper, margin=0.9in}
% document settings end

\begin{document}
\setcounter{page}{10}
\section*{Source Code}
\subsection{Array}
\subsubsection{Write a C Program to calculate sum and average of an array.}
\inputminted{C}{01.c}
\subsubsection{Write a C Program to print an array in reverse order.}
\inputminted{C}{02.c}
\subsubsection{Write a C Program to find the largest and smallest element of an array.}
\inputminted{C}{03.c}
\subsubsection{Write a C Program to find the second largest \& second smallest elements in an Array.}
\inputminted{C}{04.c}
\subsubsection{Write a C Program to Find the Largest Two Numbers in a given Array.}
\inputminted{C}{05.c}
\subsubsection{Write a C Program to divide one array into two arrays.}
\inputminted{C}{06.c}
\subsubsection{Write a C to concatenate two arrays.}
\inputminted{C}{07.c}
\subsubsection{Write a C Program to Put Even \& Odd Elements of an Array in 2 Separate Arrays.}
\inputminted{C}{08.c}
\subsubsection{Write a C Program to Read an Array and Search for an Element.}
\inputminted{C}{09.c}
\subsubsection{Write a C Program to Sort the Array in an Ascending Order.}
\inputminted{C}{10.c}
\subsubsection{Write a C Program to Sort the Array in Descending Order.}
\inputminted{C}{11.c}
\subsubsection{Write a C Program to Sort Names in an Alphabetical Order.}
\inputminted{C}{12.c}
\subsubsection{Write a C Program to Sum of two One-Dimensional Arrays.}
\inputminted{C}{13.c}
\subsubsection{Write a C Program to Sum of Two Dimensional Arrays.}
\inputminted{C}{14.c}
\subsubsection{Write a C Program to multiply of Two Dimensional Arrays.}
\inputminted{C}{15.c}
\subsubsection{Write a C Program to Insert an Element in a Specified Position in a given Array.}
\inputminted{C}{16.c}
\subsubsection{Write a C Program to Delete the Specified number from an Array.}
\inputminted{C}{17.c}
\subsection{Stack \& Queue}
\subsubsection{Write a C Program to Implement a Queue using an Array.}
\inputminted{C}{18.c}
\subsubsection{Write a C Program to Implement Stack using Array.}
\inputminted{C}{19.c}

\end{document}

