\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{geometry}
\usepackage{fancyhdr}
\usepackage{graphicx}
\usepackage{minted}
\usepackage{hyperref}

% document settings start
\geometry{a4paper, margin=0.9in}
\graphicspath{{./outputs/}}

\pagestyle{fancy}
\fancyhf{}
\lhead{Programming in C}
\rhead{Asim Bera}
\lfoot{\href{https://github.com/asimbera/ccp-assignments.git}{View on Github}}
\rfoot{Page \thepage}

\hypersetup{
colorlinks=true,
linkcolor=blue,
filecolor=magenta,
urlcolor=blue,
}
\urlstyle{same}

\input{../macro}
% document settings end

\begin{document}
\input{../cover}
\newpage
\tableofcontents
\newpage
\section{Functions}

\problem{f_01}{Write a C program to find cube of any number using function.}
\problem{f_02}{Write a C program to find diameter, circumference and area of circle using functions.}
\problem{f_03}{Write a C program to find maximum and minimum between two numbers using functions.}
\problem{f_04}{Write a C program to check whether a number is even or odd using functions.}
\problem{f_05}{Write a C program to check whether a number is prime or not using function.}
\problem{f_06}{Write a program to check whether a number is an Armstrong number or not using function.}
\problem{f_07}{WAP to check a number is perfect number or not using functions.}
\problem{f_08}{Write a C program to find all prime numbers between given interval using functions.}
\problem{f_09}{Write a C program to print all strong numbers between given interval using functions.}
\problem{f_10}{Write a C program to print all Armstrong numbers between given interval using functions.}
\problem{f_11}{Write a C program to print all perfect numbers between given interval using functions.}

\section{Recursion}

\problem{r_01}{Write a C program to find power of any number using recursion.}
\problem{r_02}{Write a C program to print all natural numbers between 1 to n using recursion.}
\problem{r_03}{Write a C program to print all even or odd numbers in given range using recursion.}
\problem{r_04}{Write a C program to find sum of all natural numbers between 1 to n using recursion.}
\problem{r_05}{Write a C program to find sum of all even or odd numbers in given range using recursion.}
\problem{r_06}{Write a C program to find reverse of any number using recursion.}
\problem{r_07}{Write a C program to check whether a number is palindrome or not using recursion.}
\problem{r_08}{Write a C program to find sum of digits of a given number using recursion.}
\problem{r_09}{Write a C program to find factorial of any number using recursion.}
\problem{r_10}{Write a C program to generate nth Fibonacci term using recursion.}
\problem{r_11}{Write a C program to find GCD (HCF) of two numbers using recursion.}
\problem{r_12}{Write a C program to find LCM of two numbers using recursion.}
\problem{r_13}{Write a C program to display all array elements using recursion.}
\problem{r_14}{Write a C program to find sum of elements of array using recursion.}
\problem{r_15}{Write a C program to find maximum and minimum elements in array using recursion.}

\end{document}

