\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{geometry}
\usepackage{fancyhdr}
\usepackage{graphicx}
\usepackage{minted}
\usepackage{hyperref}

% document settings start
\geometry{a4paper, margin=0.9in}
\graphicspath{{./outputs/}}

\pagestyle{fancy}
\fancyhf{}
\lhead{Object Oriented Programming}
\rhead{Asim Bera}
% \lfoot{\href{https://github.com/asimbera/ccp-assignments.git}{View on Github}}
\rfoot{Page \thepage}

\hypersetup{
colorlinks=true,
linkcolor=blue,
filecolor=magenta,
urlcolor=blue,
}
\urlstyle{same}

\input{../macro}
% document settings end

\begin{document}
\input{../cover}
\newpage
\tableofcontents
\newpage

\section{Assignment 3}
\problem{01}{
Create a class distance with foot and inch. Now add and subtract between
two objects of distance type
i) using objects as function argument,
ii) returning object from function}
\problem{02}{
Create a class complex as above. Now add, subtract and multiply on two
objects of complex type
i) using objects as function argument,
ii) returning object from function.
}
\problem{03}{
Create a class complex with real and imaginary part (integer). Implement
default, parameterized and copy constructor to initialize the objects of
complex class and display them.
}
\problem{04}{
Create a student class with data members as roll, name and marks with
respective data types as int, chars and float. Now create n objects of
student type and insert data into those objects. Display the student
information who got the highest mark.
}

\end{document}
