\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{geometry}
\usepackage{fancyhdr}
\usepackage{graphicx}
\usepackage{minted}
\usepackage{hyperref}

% document settings start
\geometry{a4paper, margin=0.9in}
\graphicspath{{./outputs/}}

\pagestyle{fancy}
\fancyhf{}
\lhead{Programming in C}
\rhead{Asim Bera}
\lfoot{\href{https://github.com/asimbera/ccp-assignments.git}{View on Github}}
\rfoot{Page \thepage}

\hypersetup{
colorlinks=true,
linkcolor=blue,
filecolor=magenta,
urlcolor=blue,
}
\urlstyle{same}

\input{../macro}
% document settings end

\begin{document}
\input{../cover}
\newpage
\tableofcontents
\newpage

\section{If Else}
\problem{01}{Write a C program to find maximum between two numbers.}
\problem{02}{Write a C program to find maximum between three numbers.}
\problem{03}{Write a C program to check whether a number is negative, positive or zero.}
\problem{04}{Write a C program to check whether a number is divisible by 5 and 11 or not.}
\problem{05}{Write a C program to check whether a number is even or odd.}
\problem{06}{Write a C program to check whether a year is leap year or not.}
\problem{07}{Write a C program to check whether a character is alphabet or not.}
\problem{08}{Write a C program to input any alphabet and check whether it is vowel or consonant.}
\problem{09}{Write a C program to input any character and check whether it is alphabet, digit or special character.}
\problem{10}{Write a C program to check whether a character is uppercase or lowercase alphabet.}
\problem{11}{Write a C program to input week number and print week day.}
\problem{12}{Write a C program to input month number and print number of days in that month.}
\problem{13}{Write a C program to count total number of notes in given amount.}
\problem{14}{Write a C program to input angles of a triangle and check whether triangle is valid or not.}
\problem{15}{Write a C program to input all sides of a triangle and check whether triangle is valid or not.}
\problem{16}{Write a C program to check whether the triangle is equilateral, isosceles or scalene triangle.}
\problem{17}{Write a C program to find all roots of a quadratic equation.}
\problem{18}{Write a C program to calculate profit or loss.}
\problem{19}{Write a C program to input marks of five subjects Physics, Chemistry, Biology, Mathematics and Computer. Calculate percentage and grade according to following: \\
$ Percentage >= 90\% : Grade A \\
Percentage >= 80\% : Grade B \\
Percentage >= 70\% : Grade C \\
Percentage >= 60\% : Grade D \\
Percentage >= 40\% : Grade E \\
Percentage < 40\% : Grade F $
}
\problem{20}{Write a C program to input basic salary of an employee and calculate its Gross salary according to following: \\
$ {Basic Salary} <= 10000 : HRA = 20\%, DA = 80\% \\
Basic Salary <= 20000 : HRA = 25\%, DA = 90\% \\
Basic Salary > 20000 : HRA = 30\%, DA = 95\% $
}
\problem{21}{Write a C program to input electricity unit charges and calculate total electricity bill according to the given condition: \\
For first 50 units Rs. 0.50/unit \\
For next 100 units Rs. 0.75/unit \\
For next 100 units Rs. 1.20/unit \\
For unit above 250 Rs. 1.50/unit \\
An additional surcharge of 20\% is added to the bill.
}

\end{document}

