\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{geometry}
\usepackage{fancyhdr}
\usepackage{graphicx}
\usepackage{minted}
\usepackage{hyperref}

% document settings start
\geometry{a4paper, margin=0.9in}
\graphicspath{{./outputs/}}

\pagestyle{fancy}
\fancyhf{}
\lhead{Programming in C}
\rhead{Asim Bera}
\lfoot{\href{https://github.com/asimbera/ccp-assignments.git}{View on Github}}
\rfoot{Page \thepage}

\hypersetup{
colorlinks=true,
linkcolor=blue,
filecolor=magenta,
urlcolor=blue,
}
\urlstyle{same}

\input{../macro}
% document settings end

\begin{document}
\input{../cover}
\newpage
\tableofcontents
\newpage

\section{Single Dimensional Arrays}

\problem{01}{Write a C program to read and print elements of array.}
\problem{02}{Write a C program to print all negative elements in an array.}
\problem{03}{Write a C program to find sum of all array elements.}
\problem{04}{Write a C program to find maximum and minimum element in an array.}
\problem{05}{Write a C program to count total number of even and odd elements in an array.}
\problem{06}{Write a C program to count total number of negative elements in an array.}
\problem{07}{Write a C program to copy all elements from an array to another array.}
\problem{08}{Write a C program to insert an element in an array.}
\problem{09}{Write a C program to delete an element from an array at specified position.}
\problem{10}{Write a C program to merge two array to third array.}
\problem{11}{Write a C program to find reverse of an array.}
\problem{12}{Write a C program to put even and odd elements of array in two separate array.}
\problem{13}{Write a C program to search an element in an array.}
\problem{14}{Write a C program to sort array elements in ascending or descending order.}
\problem{15}{Write a C program to left rotate an array by n positions.}
\problem{16}{Write a C program to right rotate an array by n postions.}

\end{document}

